Parameter Estimation for the CES Model

### 2013-07-19 CES.Rnw
Adjusted bounds on the graph.

<<>>=
modelUKQ_grid <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
modelUKQ_grid <- cesEst(data=dataUK, 
                        yName="iGDP", 
                        xNames=c("iCapStk", "iLabor", "iQ"), 
                        tName="iYear",
                        method="L-BFGS-B",
                        rho=seq(from=1, to=20, by=2), 
                        rho1=seq(from=1, to=2, by=0.2))
summary(modelUKQ_grid)
@

>>>>

<<>>=
modelUKQ_grid <- cesEst(data=dataUK, yName="iGDP", xNames=c("iCapStk", "iLabor", "iQ"), tName="iYear")
modelUKQ_grid <- cesEst(data=dataUK, 
                        yName="iGDP", 
                        xNames=c("iCapStk", "iLabor", "iQ"), 
                        tName="iYear",
                        method="L-BFGS-B",
                        rho=seq(from=1, to=20, by=2), 
                        rho1=seq(from=-0.5, to=2, by=0.5))
summary(modelUKQ_grid)
@
